A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-16 doc/sigchi14/targeting.tex
add result discussions, to be refined

>>>>

\subsubsection{Discussion}
\sean{to be refined}

\begin{itemize}
\item During the experiment, a lot of wireless messages were transferred for communication and logging purposes. Some messages got lost or delayed and caused the users had to redo that particular action. Infrared mode requires a lot of more handshake communications than the list mode. This means that in a more robust infrastructure, the performance of infrared mode can improve more than that of the list mode.

\item Some of the infrared performance were affected by the strength and stableness of the infrared emitter. By getting a stronger emitter that would be able to reach to a longer distance, connecting to nodes further away such as 4 and 10 would become easier.

\item As shown in figure X, the average time taken to connect to a certain client is correlated to the order of the node within the list. We therefore can assume that as the system scales, the average time required in list mode would have a linear growth. As for the infrared mode, it is more about the density of nodes in a fix space. There’s an upper bound how many smart appliance one can put on a single ta

\item In list mode, users’ eyes focuses more on the display to traverse between the list while in infrared mode, users’ eyes remain in the physical world more.

\item In our prototype, the IR emitter is nearly fixed. Due to different sizes and shapes of the users’ heads, the emitter wouldn’t necessarily point to the center of their eye sights. An adjustable emitter would even further improve the performance of our design.

\item The list mode could also be improved by making the swiping gestures more responsive, e.g. swiping speed affects traversing speed.

\item In our experiment, after users locates the nodes by ID, they can instantly figure out their names by the label provided. In realistic environments, users have to recall the names of the appliances, which would take a lot more time. Furthermore, finding names such as “Living room corner stand lamp” would be more difficult than an alphabet. On the other hand, infrared mode will most likely to be unaffected since it does not require name-recalling or text matching.

 \end{itemize}
